\textsc{PAPERCLIP}: Associating Astronomical Observations and Natural Language with Multi-Modal Models

### 2024-08-01 paper/colm_camera/colm2024_conference.tex
Typos

In this paper, we describe \text{PAPERCLIP} (Proposal Abstracts Provide an Effective Representation for Contrastive Language-Image Pre-training),
% \footnote{Technically, we fine tune rather than pre train, but ``PAPERCLIFT'' was rejected by the senior author of this paper.}), 
a method that connects, for the first time, astronomical image observations with natural language by leveraging the association between abstracts of successful observing proposals written by astronomers and images corresponding to downstream observations imaged by telescopes. 
%
\changes{This approach demonstrates the potential of adapting generalist multi-modal foundation models to astronomy, complementing task-specific models in the domain by providing a flexible, language-based interface for interacting with observational data.}
%
Concretely, we showcase the method using observations imaged by the \hubble Space Telescope (HST).
%
We show that fine-tuning a pre-trained CLIP ~\citep[Contrastive Language-Image Pre-training; ][]{radford2021learning} image-text model on observation-abstract pairs results in meaningful joint representations through quantitative and qualitative evaluation tests.
%
Our method opens up the possibility of interacting with astronomical survey data using free-form natural language as an interface, which is a cornerstone of the success of the modern foundation model paradigm. A high-level overview of the method is shown in Fig.~\ref{fig:overview}.
%

>>>>

In this paper, we describe \text{PAPERCLIP} (Proposal Abstracts Provide an Effective Representation for Contrastive Language-Image Pre-training),
% \footnote{Technically, we fine tune rather than pre train, but ``PAPERCLIFT'' was rejected by the senior author of this paper.}), 
a method that connects, for the first time, astronomical image observations with natural language by leveraging the association between abstracts of successful observing proposals written by astronomers and images corresponding to downstream observations imaged by telescopes. 
%
\changes{This approach demonstrates the potential of adapting generalist multi-modal foundation models to astronomy, complementing task-specific models by providing a flexible, language-based interface for interacting with observational data.}
%
Concretely, we showcase the method using observations imaged by the \hubble Space Telescope (HST).
%
We show that fine-tuning a pre-trained CLIP ~\citep[Contrastive Language-Image Pre-training; ][]{radford2021learning} image-text model on observation-abstract pairs results in meaningful joint representations through quantitative and qualitative evaluation tests.
%
Our method opens up the possibility of interacting with astronomical survey data using free-form natural language as an interface, which is a cornerstone of the success of the modern foundation model paradigm. A high-level overview of the method is shown in Fig.~\ref{fig:overview}.
%
